Neural models for computer-assisted musical orchestration: a preliminary study

### 2020-05-11 paper/latex/paper.tex
added back intro and changed title

%
\maketitle
%
\begin{abstract}
The abstract should be placed at the top left column and should contain about 150-200 words.
\end{abstract}
%
\section{Introduction}\label{sec:introduction}

@@

\begin{figure}
\includegraphics[scale=0.45]{CNN_LSTM_diagram.png}
\caption{Diagram of the CNN with LSTM architecture. \label{cnn_lstm}}
\end{figure}

>>>>

%
\maketitle
%
\begin{abstract}
In this paper we will explore preliminary neural models for the task of computer-assisted musical orchestration. After an introduction on the problem, we will show how we decided to model musical orchestration as a classification task. In this context, we will propose two deep learning models and we will show how they perform as classifiers for musical instruments recognition by comparing them with specific baselines. We will the show how they perform, both qualitative and quantitative, in the task of computer-assisted orchestration by comparing them with state-of-the-art systems. We will highlight, finally, benefits and problems of neural approaches for orchestration and we will propose possible future steps.
\end{abstract}
%
\section{Introduction}\label{sec:introduction}

@@

\begin{figure*}
\includegraphics[scale=0.45]{CNN_LSTM_diagram.png}
\caption{Diagram of the CNN with LSTM architecture. \label{cnn_lstm}}
\end{figure*}
